What we {\sf eval} in the shadows

### 2021-04-01 paper/main.tex
minor

The analysis presented in this has been automated by a pipeline that acquires
package code, extract metadata, executes programs, traces their behavior and
summarizes observations. Figure~\ref{fig:pipeline} shows the main steps of
analysis along with their running time, data size, and number of elements
manipulated. Timings are from a cluster of three 2.3GHz Intel Xeon 6140 servers,
with 72 cores and 256GB of RAM, and shared OCFS network storage.

>>>>

The analysis presented in this has been automated by a pipeline that acquires
packages, extract scripts, executes them, traces their behavior and summarizes
observations. Figure~\ref{fig:pipeline} shows the main steps along with their
running time, data size, and number of elements manipulated. Timings are from a
cluster of three 2.3GHz Intel Xeon 6140 servers, with 72 cores and 256GB of RAM,
and shared OCFS network storage.
